Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-11 submission.tex
Elsavier style

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }

@@

\bibitem{g7}
P.~Bermel, J.~Lee, J.~D. Joannopoulos, I.~Celanovic, and M.~Soljacie,
  \emph{Selective solar absorbers} (Begell House Inc., 2012), chap.~7, Annual
  Review of Heat Transfer.

@@

\bibitem{g14}
I.~Celanovic, N.~Jovanovic, and J.~Kassakian, \enquote{Two-dimensional tungsten
  photonic crystals as selective thermal emitters,} Appl. Phys. Lett.
  \textbf{92}, 193101 (2008).
\bibitem{g15}
H.~Wang, V.~P. Sivan, A.~Mitchell, G.~Rosengarten, P.~Phelan, and L.~Wan,
  \enquote{Highly efficient selective metamaterial absorber for
  high-temperature solar thermal energy harvesting,} Sol. Energy Mat. Sol.
  Cells \textbf{137}, 235--242 (2015).

@@

@@

\bibitem{Taflove_FDTD}
A.~Taflove and S.~C. Hagness, \emph{Computational Electrodynamics: the
  finite-difference time-domain method} (Artech, 2000).

@@

\bibitem{Yeh}
P.~Yeh, \emph{Optical waves in layered media} (Wiley, 2005).

@@

@@

@@

\bibitem{Maier}
S.~M. Maier, \emph{Plasmonics: Fundamentals and applications} (Springer, 2007).

\bibitem{Novotny}
L.~Novotny and B.~Hecht, \emph{Principles of nano-optics} (Cambridge University
  Press, 2012), 2nd ed.

@@

@@

\bibitem{real_efficient}
M.~Shimizu, A.~Kohiyama, and H.~Yugami, \enquote{{High-efficiency solar
  thermophotovoltaic system equipped with a monolithic planar selective
  absorber/emitter},} J. Photon. Energy \textbf{5}, 053099 (2015).

@@

\bibitem{lumerical}
{Lumerical Solutions, Inc.},
  \url{http://www.lumerical.com/tcad-products/mode/}.

\bibitem{YMH_PRE_2010}
M.~A. Yurkin, M.~Min, and A.~G. Hoekstra, \enquote{Applicaton of the discrete
  dipole approximation to very large refractive indices: Filtered doupled
  dipoles revived,} Phys. Rev. E \textbf{82}, 036703 (2010).

@@

\bibitem{photonic_crystal_rev}
V.~Rinnerbauer, S.~Ndao, Y.~X. Yeng, W.~R. Chan, J.~J. Senkevich, J.~D.
  Joannopoulos, M.~Soljacic, and I.~Celanovic, \enquote{Recent developments in
  high-temperature photonic crystals for energy conversion,} Energy and
  Environmental Science  (2012).
bitem{A13}
H.~Saia, H.~Yugamia, Y.~Kanamorib, and K.~Hane, \enquote{Solar selective
  absorbers based on two-dimensional {W} surface gratings with submicron
  periods for high-temperature photothermal conversion,} Sol. Energy Mat. Sol.
  Cells \textbf{79}, 35--49 (2003).

@@

\bibitem{palik}
E.~D. Palik, \emph{Handbook of optical constants of solids} (Academic Press,
  1998).

@@

\bibitem{paper2_ref6}
Y.~Xuan, X.~Chen, and Y.~Han, \enquote{Design and analysis of
  thermophotovoltaic systems,} Renew. Energ. \textbf{36}, 374--387 (2011).
\bibitem{paper2_ref13}
H.~Sai, Y.~Kanamori, K.~Hane, H.~Yugami, and M.~Yamaguchi, \enquote{Numerical
  study on tungsten selective radiators with various micro/nano structures,}
  Photovoltaic Specialists Conference pp. 762--765 (2005).

@@

\section{Introduction}
Many energy generation devices such as solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV)  \cite{g3,g4,g5} and thermophotovoltaic (TPV) \cite{g6,g7} systems require control of light absorption and emission from surfaces to achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. 
Nanostructured surfaces, for example, can be designed to be significantly
more absorbing than their flat counterparts.
Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective 
surfaces~\cite{G_PS_1985, C_RPP_2014}.  Figure \ref{gfig_bbs} shows the change in 
emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.
Some typical nanostructures are depicted schematically in Figure \ref{gfig_surfs}.

\begin{figure}[h]
	\includegraphics[width=1\textwidth]{figs/gfig_bbs}
	\caption{\label{gfig_bbs} Spectral emission of a blackbody vs. a selective emitter.} 
\end{figure}

\begin{figure}[h]
	\includegraphics[width=1\textwidth]{figs/gfig_surfs}
	\caption{\label{gfig_surfs} Types of nanostructured absorbing and 
emitting surfaces: a) random nanotexture b) periodic nanotexture and c) dielectric/metal stack.} 
\end{figure}

@@

@@

\section{Design Methodologies}

@@

Understanding how a nanostructured surface or particle absorbs, scatters, and/or reflects incident light provides
critical information enabling the design of systems for efficient solar
energy conversion.  Calculating these quantities depends upon the ability to solve Maxwell's
equations when light is incident upon nanostructures~\cite{G_JPCC_2013}.   A wide variety of theoretical 
methodologies exist for solving Maxwell's equations either in the time-domain (see for example 
Refs.~\cite{Taflove_FDTD,Meep}), 
or in the frequency domain (see for example Refs.~\cite{Bohren,Yeh,DF_JOptSocA_1994,fem}). 
Time-dependent approaches of solving Maxwell's equations 
typically start from the first-order time-dependent electric
and magnetic field equations,  whereas frequency domain methods usually take the second-order frequency-dependent wave equation, 
supplemented by appropriate boundary conditions, as their starting point.

In a few cases, Maxwell's equations  can be solved analytically; indeed, under some often
reasonable approximations, the analytical solutions can even be written simply, which
greatly aids intuition about the behavior of a nanostructure.  Two important analytical examples we will
consider include the interaction of light with spherical nanostructures, solvable by Mie
theory, and the interaction of light with planar nanostructures, solvable by the Transfer
Matrix method.   For more general structures, numerical techniques must be employed, and
several approaches have been put to considerable use.  Here we will
discuss the finite-difference time-domain (FDTD) method and the discrete dipole
approximation (DDA); the former solves Maxwell's equations in the time-domain, while the 
latter
solves them in the frequency-domain.  The finite element method, or FEM, is a  
frequency-domain approach capable of describing a greater variety of problems~\cite{fem}.
The vectorial
nature of Maxwell's equations make
implementations of FEM significantly more sophisticated than DDA.  \textcolor{blue}{Rigorous coupled-wave analysis (RCWA) represents
another frequency-domain method for solving Maxwell's equations that is particularly relevant for periodic structures~\cite{RCWA1,RCWA2}.
Although we do not discuss the RCWA method in detail, we note that it has been used successfully to design
absorber and emitter structures for TPV/STPV applications, see for example~\cite{RCWA3}.}
We will also give several
examples of applications of nanostructures for
solar energy conversion, focusing on which of the above methodologies are most
appropriate, and how they would be utilized for designing these nanostructures.

\subsection{Mie theory for spherical nanostructures}
Mie theory provides an analytical solution for Maxwell's equations when light is incident
upon a spherical particle. Analytical solutions are available for not only
homogeneous spheres but spheres composed of a core sphere with one or more outer shells, and
arbitrary complex dielectric constants may be used to define the spherical systems.   
Quantities like the absorption, scattering, and extinction cross section of the particle
can be easily computed with Mie theory. 
An excellent
discussion of Mie theory, as well as practical source code, can be found in Ref.~\cite{Bohren}.

While only rigorous for 
isolated spherical particles, judicious use of Mie theory can be an invaluable tool for modeling more complicated structures.  For instance, Mie theory can 
be adapted for very small particles that can be modeled as ellipsoids, which includes nanodisks, 
nanorods, etc.~\cite{Bohren}  Similarly, Mie theory 
can be combined with effective medium theories, e.g. Maxwell-Garnett theory, to model 
regular or random arrays of particles on a substrate, provided that the coupling 
between the neighboring particles is negligible~\cite{Bohren}.  
Extensions to effective medium theories have also
been developed that account for the impact on near-neighbor coupling on the 
polarizability of a spherical structure, 
including renormalized polarizability approaches of Moch\'{a}n and co-workers\cite{BCM_PRB_1988,BMM_PRB_1991}, and dressed
polarizability approaches of Yoo {\it et al.}\cite{YP_OptExpress_2012}.  These approaches offer similar simplicity of
using Mie theory in conjunction with an effective medium theory, but offer a more rigorous treatment of the coupled
optical response of the spherical particle to its neighbors.

\subsection{Design of nanostructures for enhancing solar energy conversion using Mie theory}
The relative simplicity of the theoretical framework describing scattering and absorption of spherical 
nanostructures affords the ability to design
systems utilizing spherical nanoparticles for a variety of solar conversion applications.  The scattering properties of
spherical nanoparticles can be leveraged to concentrate and trap incident light into thin-film photovoltaic (PV) materials to increase their
conversion efficiency.  This strategy is particularly effective if the light scattering can occur only in the forward direction, increasing
the flux of optical energy into an active PV material, for example~\cite{AP_NatMat_2010}.
Mie theory
leads to the prediction of this particularly extreme form of anisotropy where the particles scatter light only in the
forward direction when the coefficients for the electric and magnetic dipolar terms ($a_1$ and $b_1$, respectively) 
are identical, which is often called the first Kerker condition~\cite{GGG_NatComm_2012}.
Physically, this can be understood as an interference between electric
and magnetic dipolar resonances.   Because this is a resonant effect, a given particle geometry will support such scattering behavior
only at certain frequencies.  Nevertheless, Mie theory computes these coefficients directly, and it is straightforward to develop a
design protocol for spherical particles embedded in a medium with known optical properties (e.g. corresponding to the PV material, or a
compatible substrate) that support these resonances at a desired frequency.  The exceptionally large extinction cross sections
of metal nanoparticles, due to their ability to support surface plasmons, can also be exploited to efficiently trap light across
the solar spectrum.  For example, the optical response of spherical dielectric-core metal-shell nanoparticles is highly tunable, and can be
computed exactly with a generalization of Mie theory.  Halas and co-workers have employed Mie theory to
design optimal distributions of core-shell nanoparticles to enhance absorption over the AM 1.5 solar 
spectrum~\cite{CH_APL_2006}, where AM 1.5 indicates the standard for the solar 
spectrum after attenuation by Earth's atmosphere.
Using a distribution of simple silica core/gold shell particles with modest coverage allowed absorption of 84\% of incident solar power
across the AM 1.5 spectrum~\cite{CH_APL_2006}.  Figure~\ref{Halas} shows the extinction efficiency computed
by Mie theory for various core-shell particle structures.  
Similarly, resonant or near-resonant scattering effects of spherical or cylindrical 
nanostructures, including nanowires, have been modeled within the framework of Mie theory to create exceptionally strong broad-band absorbing structures~\cite{FKA_OptExp_2014}
and broad-band anti-reflection coatings~\cite{SVP_NatComm_2012}, both of which are 
widely applicable to solar conversion technologies.  
\textcolor{red}{Again, we emphasize that Mie theory is rigorous only in the limit of isolated particles, and cannot easily account for particle/interface effects. 
For such effects, more general numerical modeling approaches such as FDTD or DDA are required, and we discuss these approaches in Sections 2.6-2.8.}
\begin{figure}[h]
\begin{center}
        \includegraphics[width=\textwidth]{figs/Halas_Celanovic}
        \caption{\label{Halas}  Illustration of radiation control using engineered spherical core-shell
nanoparticles {\bf (a)} and multi-layer planar film structures {\bf (b)}.
The absorption, scattering, and extinction cross sections of the core-shell particles can be tuned
across the solar spectrum by changing the ratio of the shell thickness ($r_2$) to the core radius ($r_1$), 
and these
quantities can be computed using Mie theory (see Section {\it 2.2}) for isolated particles, or the 
DDA method (see Section {\it 2.8}) for assemblies of particles.
In {\bf (a)}, the radius of a silica core is fixed at 60 nm, and the thickness of a gold shell is
taken to be 80 nm for curve {\bf a},
70 nm for curve {\bf b}, 67 nm for curve {\bf c}, and 65 nm for curve {\bf d}.
The emittance of several multi-layer structures plotted in {\bf (b)} can be simply computed
using the Transfer Matrix Method (see Section {\it 2.4}); however, 
more sophisticated global device
efficiency considerations were used to identify a photonic crystal on a platinum substrate 
(violet curve in {\bf (b)} as the optimal emitter structure for
an integrated STPV system~\cite{g4}.
Figures reproduced from Refs.~\cite{CH_APL_2006} and~\cite{g4} with permission.}
\end{center}

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
%%\usepackage{array,multirow}
\usepackage{bm}%
\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }

@@

\bibitem{g7}
P.~Bermel, J.~Lee, J.~D. Joannopoulos, I.~Celanovic, and M.~Soljacie,
  \emph{Selective Solar Absorbers} (Begell House Inc., 2012), chap.~7, Annual
  Review of Heat Transfer.

@@

\bibitem{g14}
I.~Celanovic, N.~Jovanovic, and J.~Kassakian, \enquote{Two-dimensional tungsten
  photonic crystals as selective thermal emitters,} Appl. Phys. Lett.
  \textbf{92}, 193101 (2008).

\bibitem{g15}
H.~Wang, V.~P. Sivan, A.~Mitchell, G.~Rosengarten, P.~Phelan, and L.~Wan,
  \enquote{Highly efficient selective metamaterial absorber for
  high-temperature solar thermal energy harvesting,} Sol. Energy Mat. Sol.
  Cells \textbf{137}, 235--242 (2015).

@@

\bibitem{paper2_ref6}
Y.~Xuan, X.~Chen, and Y.~Han, \enquote{Design and analysis of
  thermophotovoltaic systems,} Renew. Energ. \textbf{36}, 374--387 (2011).

\bibitem{paper2_ref13}
H.~Sai, Y.~Kanamori, K.~Hane, H.~Yugami, and M.~Yamaguchi, \enquote{Numerical
  study on tungsten selective radiators with various micro/nano structures,}
  Photovoltaic Specialists Conference pp. 762--765 (2005).

\bibitem{Grann_JOSA}
E.~B. Grann and M.~G. Moharam, \enquote{Comparison between continuous and
  discrete subwavelength grating structures for antireflection surfaces,} J.
  Opt. Soc. Am. \textbf{13}, 988--922 (1996).

@@

\bibitem{Taflove_FDTD}
A.~Taflove and S.~C. Hagness, \emph{Computational Electrodynamics: the
  Finite-Difference Time-Domain Method} (Artech, 2000).

@@

\bibitem{Yeh}
P.~Yeh, \emph{Optical Waves in Layered Media} (Wiley, 2005).

@@

\bibitem{RCWA1}
M.~G. Moharam, D.~A. Pommet, E.~B. Grann, and T.~K. Gaylor, \enquote{Stable
  implementation of the rigorous coupled-wave analysis for surface-relief
  gratings: enhanced transmittance matrix approach,} J. Opt. Soc. A
  \textbf{12}, 1077 (1995).

\bibitem{RCWA2}
L.-L. Lin, Z.-Y. Li, and K.-M. Ho, \enquote{Lattice symmetry applied in
  transfer-matrix methods for photonic crystals,} J. Appl. Phys. \textbf{98},
  811 (2003).

\bibitem{A13}
H.~Saia, H.~Yugamia, Y.~Kanamorib, and K.~Hane, \enquote{Solar selective
  absorbers based on two-dimensional {W} surface gratings with submicron
  periods for high-temperature photothermal conversion,} Sol. Energy Mat. Sol.
  Cells \textbf{79}, 35--49 (2003).

\bibitem{RCWA3}
V.~Rinnerbauer, Y.~Shen, J.~D. Joannopolous, M.~Solja{\v c}i{\' c}, F.~Sch{\"
  a}ffler, and I.~Celanovic, \enquote{Superlattice photonic crystal as
  broadband solar absorber for high temperature operation,} Opt. Express
  \textbf{22}, A1895 (2014).

@@

\bibitem{FMS_ACSPhoton_2014}
J.~J. {Foley IV}, J.~M. McMahon, G.~C. Schatz., H.~Harutyunyan, G.~P.
  Wiederrecht, and S.~K. Gray, \enquote{Inhomogeneous surface plasmon
  polaritons,} ACS Photonics \textbf{1}, 739--745 (2014).

\bibitem{CWH_JQSRT_2005}
P.~C. Chang, J.~G. Walker, and K.~I. Hopcraft, \enquote{Ray tracing in
  absorbing media,} J. Quant. Spectrosc. Radiat. Transfer \textbf{96}, 327--341
  (2005).

@@

\bibitem{Maier}
S.~M. Maier, \emph{Plasmonics: Fundamentals and Applications} (Springer, 2007).

\bibitem{Novotny}
L.~Novotny and B.~Hecht, \emph{Principles of Nano-Optics} (Cambridge
  University, 2012), 2nd ed.

@@

\bibitem{Raether}
H.~Raether, \emph{Surface Plasmons on Smooth and Rough Surfaces and on
  Gratings} (Springer-Verlag, 1988).

@@

@@

\bibitem{lumerical}
{Lumerical Solutions, Inc.},
  \url{http://www.lumerical.com/tcad-products/mode/}.
\bibitem{YMH_PRE_2010}
M.~A. Yurkin, M.~Min, and A.~G. Hoekstra, \enquote{Applicaton of the discrete
  dipole approximation to very large refractive indices: Filtered doupled
  dipoles revived,} Phys. Rev. E \textbf{82}, 036703 (2010).

@@

\bibitem{photonic_crystal_rev}
V.~Rinnerbauer, S.~Ndao, Y.~X. Yeng, W.~R. Chan, J.~J. Senkevich, J.~D.
  Joannopoulos, M.~Soljacic, and I.~Celanovic, \enquote{Recent developments in
  high-temperature photonic crystals for energy conversion,} Energy and
  Environmental Science  (2012).

@@

\bibitem{palik}
E.~D. Palik, \emph{Handbook of Optical Constants of Solids} (Academic, 1998).

@@

@@

%%\bibliography{submission}

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5}, and thermophotovoltaic (TPV) \cite{g6,g7} energy conversion.  To provide a state of the art status in 
these fields, we have prepared this review article.  There is strong potential for growth in these areas, especially 
through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to 
achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, 
which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. 
Nanostructured surfaces, for example, can be designed to be significantly
more absorbing than their flat counterparts.
Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective 
surfaces~\cite{G_PS_1985, C_RPP_2014}.  Figure \ref{gfig_bbs} shows the change in 
emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.
Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy.  This allows them to be used in energy reclamation systems.

\begin{figure}[ht]
	\includegraphics[width=1\textwidth]{gfig_bbs}
	\caption{\label{gfig_bbs} Spectral emission of a blackbody vs. a selective emitter.  Note that the scales on each graph are in different arbitrary units; the graph is intended to show the relative narrowness of the spectrum using the selective emitter.}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=1\textwidth]{gfig_surfs}
	\caption{\label{gfig_surfs} Types of nanostructured absorbing and 
emitting surfaces: a) random nanotexture b) periodic nanotexture and c) dielectric/metal stack.} 
\end{figure}

@@

The limiting efficiency for ST and STPV systems with ideal absorbing and emitting surfaces comes from the Carnot efficiency ($\eta$) 
given by $\eta = 1 - \frac{T_c}{T_h}$, where $T_c$ and $T_h$ are the hot and cold temperatures, respectively. The absorbing 
surface efficiency is lowered due to radiative loss, 
given by $ A \epsilon \sigma T^4$, where $A$ is the area, $\epsilon$ is emissivity, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature.  
While the Carnot efficiency of the system will increase with temperature, the absorbing surface efficiency will decrease due to 
increased emission from the absorbing surface at high operating temperatures~\cite{L_AIP_2007}.  The maximum operating efficiency 
of 85.4\% is therefore reached at an operating temperature of 2600 K in the ideal case for both systems.  Increasing 
the temperature beyond this will result in a decrease in system efficiency.  This analysis assumes that incoming 
radiation is concentrated to the maximum achievable solar concentration of 46000x.  At this concentration, the 
ideal surface is simply a blackbody absorber.

As the solar concentration is decreased, the ideal surface will be a blackbody absorber for wavelengths below 
some $\lambda_{cutoff}$, and an ideal reflector (generating lower emission) for wavelengths above the cutoff.  The 
location of $\lambda_{cutoff}$
depends on the temperature of the system, the power density of the emission from the emitter, and the solar concentration 
levels achieved in the system.  Typical $\lambda_{cutoff}$ values will be close to 2 $\mu m$ due to the importance of absorbing a 
large portion of the solar spectrum~\cite{RF_OptExp_2009}.

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

The temperature of 1000$^\circ$C was an upper limit chosen for practical ST systems based off existing 
technologies~\cite{RKR_RenEnRev_2013, g2}.  This temperature was chosen for the purpose of comparing different nanostructured 
surfaces suitable for incorporation into ST systems.  The performance of ST systems will generally 
increase up to a specific temperature~\cite{MS_EnConvMan_2012}.  The value of this temperature is dependent on the 
quality of surfaces used and the solar concentration value achieved.  For tower-based (high-concentration) 
ST systems, this temperature is usually significantly above current operating temperatures, resulting in a 
desire for increased thermal stability. Most materials degrade at high temperatures for extended period of 
operation, so a reasonable number of 1000$^{\circ}$ was assumed. This number is consistent with temperature used in 
many solar thermal applications as well as for thermophotovoltaics.

Figure \ref{gfig_surfs} shows different kinds of nanostructures used to create spectrally selective surfaces in energy generation systems.  Random and periodic nanostructures may have different shapes depending on the fabrication method used.  Triangular, sawtooth, square, spherical, and cylindrical structures all see use in these systems \cite{global_opt,paper2_ref6,RF_OptExp_2009}.  Additionally, spherical or obloid nanostructures may be embedded in a dielectric matrix to selectively scatter specific wavelengths of light.  Lastly, as shown in Figure 2c, planar dielectric or dielectric and metal stacks may be used.

Melting point depression and thermal mismatching between layers makes temperature stability a major concern for spectrally selective surfaces.  This issue is solved primarily through material selection and the use of protective coatings on nanostructured materials \cite{paper1_ref5}.  Smaller nanostructures and thinner layers can increase this effect, resulting in a limited design space for some nanomaterials.

The type of nanostructure used in a system can have a large impact on its ease of fabrication, spectral selectivity, and temperature stability.  The use of random elements in nanostructures eases fabrication tolerance requirements and can improve selectivity, but can be difficult to design for or simulate properly \cite{me1}.  The presence of some smaller--period nanostructures can lead to lower thermal stability in random nanostructures as well.

Square and cylindrical type gratings result in a rapid change in index of refraction (as compared to tapered structures) that can result in low visible or near infrared (IR) emittance and narrow absorption peaks \cite{paper1_ref6,paper2_ref13}.  This can be a boon to the design of narrow-band emitter structures, or a hindrance to the design of solar absorbing surfaces.  Combinations of multiple periods of gratings can be used to broaden the emittance peaks in these structures; however, they still lack high emission in the near IR and visible regions \cite{paper2_ref14}.  Using conical, sawtooth, or triangular type nanostructures can increase short-wavelength emission due to the more gradual change in index throughout the structure \cite{Grann_JOSA,me2}.
Planar surfaces using thin layers of multiple different dielectrics suffer from relatively broad absorption peaks.  The inclusion of a metallic layer or the addition of many dielectric layers can result in a much more narrow emission peak \cite{RF_OptExp_2009}.

@@

\section{Design methodologies}

@@

Understanding how a nanostructured surface or particle absorbs, scatters, and/or reflects incident light provides
critical information enabling the design of systems for efficient solar
energy conversion.  Calculating these quantities depends upon the ability to solve Maxwell's
equations when light is incident upon nanostructures~\cite{G_JPCC_2013}.   A wide variety of theoretical 
methodologies exist for solving Maxwell's equations either in the time-domain (see for example 
\cite{Taflove_FDTD,Meep}), 
or in the frequency domain (see for example~\cite{Bohren,Yeh,DF_JOptSocA_1994,fem,RCWA1,RCWA2}). 
Time-dependent approaches of solving Maxwell's equations 
typically start from the first-order time-dependent electric
and magnetic field equations,  whereas frequency domain methods usually take the second-order frequency-dependent wave equation, 
supplemented by appropriate boundary conditions, as their starting point.

In a few cases, Maxwell's equations  can be solved analytically; indeed, under some often
reasonable approximations, the analytical solutions can even be written simply, which
greatly aids intuition about the behavior of a nanostructure.  Two important analytical examples we will
consider include the interaction of light with spherical nanostructures, solvable by Mie
theory, and the interaction of light with planar nanostructures, solvable by the Transfer
Matrix method.   For more general structures, numerical techniques must be employed, and
several approaches have been put to considerable use.  Here we will
discuss the finite-difference time-domain (FDTD) method and the discrete dipole
approximation (DDA); the former solves Maxwell's equations in the time-domain, while the 
latter
solves them in the frequency-domain. Two other frequency-domain approaches, that
we do not focus in detail on, should also be noted.  The finite element method, or FEM, is a  
frequency-domain approach capable of describing a greater variety of 
problems than DDA~\cite{fem}.
The vectorial
nature of Maxwell's equations make
implementations of FEM significantly more sophisticated than DDA.  Rigorous coupled-wave analysis (RCWA) represents
another frequency-domain method for solving Maxwell's equations that is 
particularly relevant for periodic structures~\cite{RCWA1,RCWA2} and, 
because of its efficiency, has been used successfully to design a number of
absorber and emitter structures for TPV/STPV applications, 
see for example~\cite{A13, RCWA3}.  In what follows we will also give several
examples of applications of nanostructures for
solar energy conversion, focusing on which of the above methodologies are most
appropriate, and how they would be utilized for designing these nanostructures.

\subsection{Mie theory for spherical nanostructures}
Mie theory provides an analytical solution for Maxwell's equations when light is incident
upon a spherical particle. Analytical solutions are available for not only
homogeneous spheres but spheres composed of a core sphere with one or more outer shells, and
arbitrary complex dielectric constants may be used to define the spherical systems.   
Quantities like the absorption, scattering, and extinction cross section of the particle
can be easily computed with Mie theory. 
An excellent
discussion of Mie theory, as well as practical source code, can be found in~\cite{Bohren}.

While only rigorous for 
isolated spherical particles in homogeneous media, judicious use of Mie theory can be an invaluable tool for modeling more complicated structures.  For instance, Mie theory can 
be adapted for very small particles that can be modeled as ellipsoids, which includes nanodisks, 
nanorods, etc.~\cite{Bohren}  Similarly, Mie theory 
can be combined with effective medium theories, e.g. Maxwell-Garnett theory, to model 
regular or random arrays of particles on a substrate, provided that the coupling 
between the neighboring particles is negligible~\cite{Bohren}.  
Extensions to effective medium theories have also
been developed that account for the impact on near-neighbor coupling on the 
polarizability of a spherical structure, 
including renormalized polarizability approaches of Moch\'{a}n and co-workers\cite{BCM_PRB_1988,BMM_PRB_1991}, and dressed
polarizability approaches of Yoo {\it et al.}\cite{YP_OptExpress_2012}.  These approaches offer similar simplicity of
using Mie theory in conjunction with an effective medium theory, but offer a more rigorous treatment of the coupled
optical response of the spherical particle to its neighbors.

\subsection{Design of nanostructures for enhancing solar energy conversion using Mie theory}
The relative simplicity of the theoretical framework describing scattering and absorption of spherical 
nanostructures affords the ability to design
systems utilizing spherical nanoparticles for a variety of solar conversion applications.  The scattering properties of
spherical nanoparticles can be leveraged to concentrate and trap incident light into thin-film photovoltaic (PV) materials to increase their
conversion efficiency.  This strategy is particularly effective if the light scattering can occur only in the forward direction, increasing
the flux of optical energy into an active PV material, for example~\cite{AP_NatMat_2010}.
Mie theory
leads to the prediction of this particularly extreme form of anisotropy where the particles scatter light only in the
forward direction when the coefficients for the electric and magnetic dipolar terms ($a_1$ and $b_1$, respectively) 
are identical, which is often called the first Kerker condition~\cite{GGG_NatComm_2012}.
Physically, this can be understood as an interference between electric
and magnetic dipolar resonances.   Because this is a resonant effect, a given particle geometry will support such scattering behavior
only at certain frequencies.  Nevertheless, Mie theory computes these coefficients directly, and it is straightforward to develop a
design protocol for spherical particles embedded in a medium with known optical properties (e.g. corresponding to the PV material, or a
compatible substrate) that support these resonances at a desired frequency.  The exceptionally large extinction cross sections
of metal nanoparticles, due to their ability to support surface plasmons, can also be exploited to efficiently trap light across
the solar spectrum.  For example, the optical response of spherical dielectric-core metal-shell nanoparticles is highly tunable, and can be
computed exactly with a generalization of Mie theory.  Halas and co-workers have employed Mie theory to
design optimal distributions of core-shell nanoparticles to enhance absorption over the AM 1.5 solar 
spectrum~\cite{CH_APL_2006}, where AM 1.5 indicates the standard for the solar 
spectrum after attenuation by Earth's atmosphere.
Using a distribution of simple silica core/gold shell particles with modest coverage allowed absorption of 84\% of incident solar power
across the AM 1.5 spectrum~\cite{CH_APL_2006}.  Figure~\ref{Halas} shows the extinction efficiency computed
by Mie theory for various core-shell particle structures.  
Similarly, resonant or near-resonant scattering effects of spherical or cylindrical 
nanostructures, including nanowires, have been modeled within the framework of Mie theory to create exceptionally strong broad-band absorbing structures~\cite{FKA_OptExp_2014}
and broad-band anti-reflection coatings~\cite{SVP_NatComm_2012}, both of which are 
widely applicable to solar conversion technologies.  Again, we emphasize 
that Mie theory is rigorous only in the limit of isolated particles 
in homogeneous media
and cannot easily account for particle/interface effects.
For such effects, more general numerical modeling approaches such as FDTD or DDA are required, and we discuss these approaches in Sections 2.6-2.8.

\begin{figure}[ht]
\begin{center}
        \includegraphics[width=\textwidth]{Halas_Celanovic}
        \caption{\label{Halas}  Illustration of radiation control using engineered spherical core-shell
nanoparticles {\bf (a)} and multi-layer planar film structures {\bf (b)}.
The absorption, scattering, and extinction cross sections of the core-shell particles can be tuned
across the solar spectrum by changing the ratio of the shell thickness ($r_2$) to the core radius ($r_1$), 
and these
quantities can be computed using Mie theory (see Section {\it 2.2}) for isolated particles, or the 
DDA method (see Section {\it 2.8}) for assemblies of particles.
In {\bf (a)}, the radius of a silica core is fixed at 60 nm, and the thickness of a gold shell is
taken to be 80 nm for curve {\bf a},
70 nm for curve {\bf b}, 67 nm for curve {\bf c}, and 65 nm for curve {\bf d}.
The emittance of several multi-layer structures plotted in {\bf (b)} can be simply computed
using the Transfer Matrix Method (see Section {\it 2.4}); however, 
more sophisticated global device
efficiency considerations were used to identify a photonic crystal on a platinum substrate 
(violet curve in {\bf (b)} as the optimal emitter structure for
an integrated STPV system~\cite{g4}.
Figures reproduced from~\cite{CH_APL_2006} and~\cite{g4} with permission.}
\end{center}
\end{figure}
